---
title: "Course Project 1"
output: html_document
---

Loading and preprocessing the data

```{r setoptions, echo=TRUE}
data<-read.csv('activity.csv',sep=',',header=TRUE,na.strings = NA)
library(ggplot2)
col1<-colorRampPalette(c('red','yellow'),alpha=0.3)
```

##What is mean total number of steps taken per day?

1.Calculate the total number of steps taken per day
```{r}
step_day<-aggregate(steps~date,data=data,sum,na.rm=TRUE)
```


2.Make a histogram of the total number of steps taken each day
```{r}
g<-ggplot(data=step_day)
g+aes(steps)+geom_histogram(breaks=seq(0,25000,by=5000),fill=col1(10)[8])
```

3.the mean and median of the total number of steps taken per day
```{r }
mean(step_day$steps)
median(step_day$steps)
#sum_step_per_day
```
>the mean of the total number of steps taken per day is __`r mean(step_day$steps)`__

>the median of the total number of steps taken per day is __`r median(step_day$steps)`__


##What is the average daily activity pattern?

1.Make a time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r }
step_interval<-aggregate(steps~interval,data=data,mean,na.rm=TRUE)

g<-ggplot(data=step_interval)
g+aes(interval,steps)+geom_line(colour=col1(10)[2])+ylab('avg_step')+ggtitle('avg_step per interval')
```

2.Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r }
step_interval[which.max(step_interval$steps),]$interval
```
the maximum number of steps is __`r step_interval[which.max(step_interval$steps),]$interval`__th


##Imputing missing values

1.Calculate and report the total number of missing values in the dataset

```{r}
sum(is.na(data$steps))
```
the total number of missing values is __`r sum(is.na(data$steps))`__

2.Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.


```{r}
names(step_interval)<-c('interval','avg_step')
data1<-merge(data,step_interval,by='interval')
```

3.Create a new dataset that is equal to the original dataset but with the missing data filled in.

```{r}
data1[is.na(data1$steps),]['steps']<-data1[is.na(data1$steps),]['avg_step']
```

4.1 Make a histogram of the total number of steps taken each day 

```{r}
step_day1<-aggregate(steps~date,data=data1,sum,na.rm=TRUE)

g<-ggplot(data=step_day1)
g+aes(steps)+geom_histogram(breaks=seq(0,25000,by=5000),fill=col1(10)[8])
```

4.2 Do these values differ from the estimates from the first part of the assignment? 

__YES!__

4.3 What is the impact of imputing missing data on the estimates of the total daily number of steps?

__it will be more concentrate on the center of data__


##5.Are there differences in activity patterns between weekdays and weekends?

1.Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.
```{r}
data1$weekday=ifelse(as.POSIXlt(as.Date(data1$date))$wday%%6==0,'weekend','weekday')
data1$day=factor(data1$weekday,levels=c("weekday","weekend"))
```

2.Make a panel plot containing a time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis). 

```{r}
step_interval1<-aggregate(steps~interval+weekday,data=data1,mean,na.rm=TRUE)

g<-ggplot(data=step_interval1)
g+aes(interval,steps)+geom_line(colour=col1(10)[2])+ylab('avg_step')+ggtitle('avg_step per interval')+facet_grid(weekday~.)

```

See the README file in the GitHub repository to see an example of what this plot should look like using simulated data.



